Should geophysicists use the gravity disturbance or the anomaly?

### 2018-05-29 manuscript/letter.tex
rephrase the sentence about the sphere

\author[Hallam et al.]{
\parbox{\linewidth}{%
    Kristoffer A. T. Hallam$^{1}$\thanks{Emails: kristoffer.hallam@gmail.com, vanderlei@on.br},
    Vanderlei C. Oliveira Jr$^1$,
    Val\'{e}ria C. F. Barbosa$^1$, and \linebreak Leonardo Uieda$^2$
    \vspace{0.3cm}
}%
    \\
    $^1$ Department of Geophysics, Observat\'{o}rio Nacional, Rio de Janeiro, Brazil \\
    $^2$ Department of Geology and Geophysics, SOEST, University of Hawai'i at M\={a}noa, Honolulu, USA
}

@@

More often than not, gravity modelling is done by computing the
vertical component of the gravitational acceleration exerted by the sources.
We have shown that, in doing so, one is actually computing the gravity
disturbance while attempting to fit a gravity anomaly.
This is a clear inconsistency.
Doing so may even result in wrong interpretations of a quantitative nature.
In Brazil, for example, the maximum difference
between the gravity disturbance and the free-air anomaly reaches $\approx 9.3$ mGal.
Such difference at the Earth's surface may lead to
an error of $850$ m in the depth-to-center estimate of a sphere with true depth-to-center at $700$ m, radius $699$ m, and density contrast of $600 kg.m^{-3}$.

>>>>

\author[Hallam et al.]{
\parbox{\linewidth}{%
    Vanderlei C. Oliveira Jr$^1$\thanks{Email: vanderlei@on.br},
    Leonardo Uieda$^2$, Val\'{e}ria C. F. Barbosa$^1$, and
    \linebreak Kristoffer A. T. Hallam$^{1}$ 
    \vspace{0.3cm}
}%
    \\
    $^1$ Department of Geophysics, Observat\'{o}rio Nacional, Rio de Janeiro, Brazil \\
    $^2$ Department of Geology and Geophysics, SOEST, University of Hawai'i at M\={a}noa, Honolulu, USA
}

@@

More often than not, gravity modelling is done by computing the
vertical component of the gravitational acceleration exerted by the sources.
We have shown that, in doing so, one is actually computing the gravity
disturbance while attempting to fit a gravity anomaly.
This is a clear inconsistency.
Doing so may even result in wrong interpretations of a quantitative nature.
In Brazil, for example, the maximum difference
between the gravity disturbance and the free-air anomaly reaches $\approx 9.3$ mGal.
This is approximately the maximum difference between the vertical gravitational 
accelerations of a sphere with depth-to-center of $700$ m and one with $1550$ m, 
assuming both spheres have a radius of $699$ m and density contrast of 
$600$ kg~$\cdot$~m~$^{-3}$.
